A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-24 05_severity_metaAnalysis.Rmd
Ammend table

```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$trial, PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   group_by(Var2) %>%
   summarise(n()) %>%
   pull()

# create data.frame
results_mv <- data.frame(
   moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Recommended",
   "Recommended+",
   "Late",
   "Late+"
   ),
   N = PMsev_mv$g.levels.k,
   k = k5,
   Effect = round(PMsev_mv$b, 4),
   se = round(PMsev_mv$se, 4),
   CI_lower = round(PMsev_mv$ci.lb, 4),
   CI_upper = round(PMsev_mv$ci.ub, 4),
   z_val = round(PMsev_mv$zval, 4),
   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
)

# rename colnames to give table headings
colnames(results_mv)[c(2:5, 7:10)] <-
   c("Treatment",
     "N",
     "k",
     "mu",
     "CI_{L}",
     "CI_{U}",
     "Z",
     "P")

disease_estimates_table <- 
   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
   align(j = 3:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption("Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept.") %>%
   autofit()

>>>>

```{r metafor_results}
# obtain number of treatments included in each moderator variable
k5 <-
   as.data.frame(table(PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   group_by(Var2) %>%
   summarise(n()) %>%
   pull()

k6 <-
   as.data.frame(table(PM_dat_D$trial_ref, PM_dat_D$spray_management)) %>%
   filter(Freq != 0) %>%
   group_by(Var2) %>%
   summarise(n()) %>%
   pull()

intercept <- round(PMsev_mv$b, 4)[1,1]

# create data.frame
results_mv <- data.frame(
   Moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Late",
   "Late+",
   "Recommended",
   "Recommended+"
   ),
   N = k5,
   k = k6,
   Effect = round(PMsev_mv$b, 4),
   se = round(PMsev_mv$se, 4),
   CI_lower = round(PMsev_mv$ci.lb, 4),
   CI_upper = round(PMsev_mv$ci.ub, 4),
   z_val = round(PMsev_mv$zval, 4),
   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE),
   eff_bar = round(1 -(intercept + PMsev_mv$b)/intercept,4)*100,
   eff_CI_low = round(1 -(intercept + PMsev_mv$ci.lb)/intercept,4)*100,
   eff_CI_high = round(1 -(intercept + PMsev_mv$ci.ub)/intercept,4)*100
)

# rename colnames to give table headings
colnames(results_mv)[c(1:4,6:12 )] <-
   c("Moderator",
     "N",
     "k",
     "mu",
     "CI_{L}",
     "CI_{U}",
     "Z",
     "P",
     "Efficacy",
     "Eff CI upper",
     "Eff CI_lower")

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1:4,6:7, 9:12)]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:10),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Fungicide spray schedule efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )
